Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-09-03 prop_letter.tex
comments

To explain why this result is equivalent to the original
Kochen-Specker theorem and to prove it at the same time, we proceed by
assuming a 0-deterministic QIVPM $\bar{\mu}$ and derive a
contradiction to the original Kochen-Specker theorem using the same
nine observables $\mathbf{O}_{ij}$ with both $i$ and $j$ in the range
${1,2,3}$ used in the ``Mermin-Peres'' proof of the Kochen-Specker
theorem~\cite{Mermin1990Simple,peres1995quantum}. These nine
observables are given below: {\renewcommand{\arraystretch}{2}%
\begin{center}
\begin{tabular}{|@{\quad}c@{\quad}|@{\quad}c@{\quad}|@{\quad}c@{\quad}|}
\hline 
$\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\mathbb{1}$  & $\sigma_{z}\otimes\sigma_{z}$ \tabularnewline
\hline 
$\sigma_{x}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{x}\otimes\sigma_{x}$ \tabularnewline
\hline 
$\sigma_{x}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$ \tabularnewline
\hline 
\end{tabular}\,,
\par\end{center}
}
\noindent where
$\left\{\mathbb{1},\sigma_{x},\sigma_{y},\sigma_{z}\right\}$ are the
Pauli matrices acting on a pair of spin-$\frac{1}{2}$ states. These
matrices satisfy
$\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
Furthermore we have that the observables in the square satisfy the
following properties: each observable has expectation value~$1$
or~$-1$; in each row and column, the observables commute; and in each
row and column except the third column, each operator is the product
of the other two. To find a QIVPM~$\bar{\mu}$ \ldots

>>>>

\amr{Start comments}

2 qubit system
otimes is tensor product
mathbb{1} is identity projector/observable/matrix
expectation value relative to mubar
explain why expectation value of 0-determinstic qivpm is eigen value
of observable

To explain why this result is equivalent to the original
Kochen-Specker theorem and to prove it at the same time, we proceed by
assuming a 0-deterministic QIVPM $\bar{\mu}$ and derive a
contradiction to the original Kochen-Specker theorem using the same
nine observables $\mathbf{O}_{ij}$ with both $i$ and $j$ in the range
$\{1,2,3\}$ used in the ``Mermin-Peres'' proof of the Kochen-Specker
theorem~\cite{Mermin1990Simple,peres1995quantum}. These nine
observables are given below: {\renewcommand{\arraystretch}{2}%
\begin{center}
\begin{tabular}{|@{\quad}c@{\quad}|@{\quad}c@{\quad}|@{\quad}c@{\quad}|}
\hline 
$\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\mathbb{1}$  & $\sigma_{z}\otimes\sigma_{z}$ \tabularnewline
\hline 
$\sigma_{x}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{x}\otimes\sigma_{x}$ \tabularnewline
\hline 
$\sigma_{x}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$ \tabularnewline
\hline 
\end{tabular}\,,
\par\end{center}
}
\noindent where
$\left\{\mathbb{1},\sigma_{x},\sigma_{y},\sigma_{z}\right\}$ are the
Pauli matrices acting on a pair of spin-$\frac{1}{2}$ states. These
matrices satisfy
$\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
Furthermore we have that the observables in the square satisfy the
following properties: each observable has expectation value~$1$
or~$-1$; in each row and column, the observables commute; and in each
row and column except the third column, each operator is the product
of the other two. To find a QIVPM~$\bar{\mu}$ \ldots
